Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-05-20 causal-bandit/nips_2016/tech.tex
fixes reference for chernof bound

Assume without loss of generality that $q_1 \leq q_2 \leq \ldots \leq q_N \leq 1/2$. The assumption is non-restrictive since all variables
are independent and permutations of the variables can be pushed to the reward function.
The proof of Theorem \ref{thm:uq-simple} requires some lemmas, the first of which is an immediate consequence of the Chernoff bound (see Exercise 2.10 in \cite{boucheron2013concentration} for this form of the Chernoff bound).

@@

\begin{lemma}\label{lem:conc2}
Let $X_1,X_2\ldots,$ be a sequence of random variables with $X_i \in [0,1]$ and $\EE X_i = p$ and $\delta \in [0,1]$.
Then 
\eq{
\P{\exists t \geq n_0 : \left|\frac{1}{t} \sum_{s=1}^t X_s - p\right| \geq \sqrt{\frac{2}{n_0} \log \frac{2}{\delta}}} \leq 4\delta\,.
}
\end{lemma}

>>>>

Assume without loss of generality that $q_1 \leq q_2 \leq \ldots \leq q_N \leq 1/2$. The assumption is non-restrictive since all variables
are independent and permutations of the variables can be pushed to the reward function.
The proof of Theorem \ref{thm:uq-simple} requires some lemmas. \

@@

\begin{proof}
By definition, $\hat{q}_i = \frac{2}{T}\sum_{t=1}^{T/2}X_{t,i}$, where $X_{t,i} \sim Bernoulli(q_i)$. Therefore from the Chernoff bound (see equation 6 in \cite{hagerup1990guided}),

\eq{
\P{\left|\hat q_i - q_i\right| \geq \epsilon} \leq 2e^{-\frac{T\epsilon^2}{6q_i}}
}

Letting $\delta = 2e^{-\frac{T\epsilon^2}{6q_i}}$ and solving for $\epsilon$ completes the proof.

\end{proof}

\begin{lemma}\label{lem:conc2}
Let $X_1,X_2\ldots,$ be a sequence of random variables with $X_i \in [0,1]$ and $\EE[X_i] = p$ and $\delta \in [0,1]$.
Then 
\eq{
\P{\exists t \geq n_0 : \left|\frac{1}{t} \sum_{s=1}^t X_s - p\right| \geq \sqrt{\frac{2}{n_0} \log \frac{2}{\delta}}} \leq 4\delta\,.
}
\end{lemma}
